\pagenumbering{arabic}
\chapter{Introduction}

\section{Background}
The Institute of Engineering Purwanchal Campus (IOEPC) is the leading technical education institution in Nepal and offers undergraduate and graduate programs in various fields of engineering, such as civil engineering, mechanical engineering, electrical engineering, electronics and communication engineering, computer engineering, and architecture. It currently carries out administrative and academic tasks both offline and online. While most academic notices are published through social media, including daily routines, this causes important notices to be missed and reliance on third-party software. Moreover, there is a lack of a centralized website or application to access all college-related work. To address this, we propose the development of a mobile application that can integrate all college services and is flexible for future enhancements. Our aim is to provide a convenient and efficient platform for college students while ensuring easy integration of existing offline processes. We anticipate that this application will be highly advantageous to the Institute of Engineering.

\section{Gap Identification}
\begin{itemize}
    \item The current services of IOEPC are mostly manual and offline, leading to delays and inefficiencies.
    \item The current system lacks real-time updates and fails to provide timely and relevant information to students; the class schedule is heavily reliant on the class representative.
    \item Dependency on social media causes some important notices, like late fee notices, to be missed.
    \item The library management is not integrated and is run separately.
    \item A modernized system, such as a mobile app, is needed to provide a centralized platform for communication, access to course materials, and other relevant resources.
\end{itemize}

\section{Motivation}
The Campus Connect app is inspired by the difficulties we faced during our time in college. The inconsistencies between the services provided by the campus and their accessibility have been the driving force. A student isn’t aware when fee notices are published if they don’t come across a specific Facebook post. Teachers canceling classes at the last minute, while failing to convey it to the class representative, causes commuting students hassle.

\section{Objectives}
\begin{itemize}
    \item To create an easily scalable and integrable college application.
    \item To improve online access to the educational system and mitigate current problems by using monolithic architecture.
\end{itemize}