\chapter{LITERATURE REVIEW}

In 2010, JetBrains created Kotlin to enhance the Java Virtual Machine experience for the user. It supports both object-oriented and functional programming paradigms. With the support of non-nullable types, the applications are immune to null pointer exceptions. Furthermore, Kotlin appeared as the most loved language in the Stack Overflow developer survey for the year 2018 and 2019 \cite{oliveira2020adoption}.

The monolithic architecture has every service of the application interconnected and has a very modular architecture and good decoupling between their internal components. In terms of Node.js, all the services are part of the same code base and run in a single process \cite{casciaro2020nodejs}.

\section{Related Work}
An Android App for Kathmandu University displays information about the university, university calendar, course registration, applying for transcripts, news, notices, and student activities. It provides information about student welfare, the central library, publication, and research of the university. This app brings all the major components of their website into a single dashboard with added benefits of personalization \cite{kathmandu2025app}.

An application for The British College (Student Portal) displays the courses’ schedule and exams schedule for students from anywhere and anytime, also notifying the students of student lectures’ schedule and exams automatically, viewing the academic information and grades report (marks transcript) for the students. This system depends on the university website directly.